---
title: "Homework 12"
author: "Kimberly McNeil"
date: "4/24/2026"
output:
  html_document:
    code_folding: hide
linkcolor: blue
urlcolor: blue
---

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(
  echo = TRUE#, 
  #warning=FALSE, 
  #message=FALSE
  )
library(knitr)
library(dplyr)
library(readxl)
library(writexl)
library(DBI)
library(duckdb)
library(tidyverse)
```

# Penguin Excel Spreadsheet

## Load Worksheets

Let's load the three spreadsheets from the Excel file into separate tibbles, taking care that the data types import correctly:^[Question 1 Complete]
```{r}
penguins_1 = read_excel("penguins.xlsx", sheet = 1, na = "NA")
penguins_2 = read_excel("penguins.xlsx", sheet = 2, na = "NA")
penguins_3 = read_excel("penguins.xlsx", sheet = 3, na = "NA")
```

## Stack the Data

Now, let's combine the three datasets into one, longer tibble:^[Question 2 Complete]
```{r}
penguins = bind_rows(penguins_1, penguins_2, penguins_3)
```

## Bill Measurements Scatterplot

The following scatterplot showcases bill depth versus bill length, colored by species, faceted by island:^[Question 3 Complete]
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, color = species)) +
  geom_point() +
  facet_wrap(~island) +
  labs(
    title = "Bill Depth vs. Bill Length by Species (Color) and Island (Sections)",
    x = "Bill Length (mm)",
    y = "Bill Depth (mm)"
  )
```










